\bf Model Visualization Techniques for a Social Network Model

### 2017-08-19 paper.Rnw
it compiles. Through to section 4.

<<sienagof, fig.cap="Goodness of fit measures for two network statisticscomputed on the first simulated wave of a SAOM: indegree and outdegree cumulative distributions. On the x-axis is the degree value, and on the y-axis is the number of times that degree value occurs in the network. \\st{The p-value shown on the x-axis is the proportion of observations simulated from the model that have observed statistic values as large or larger than the values observed in the data.}", cache = TRUE, message = FALSE, warning = FALSE, fig.height=3>>=
load("data/ansnullpaper.rda")
library(lattice)
gof1 <- sienaGOF(ansnull, OutdegreeDistribution, varName ="friendship", join = FALSE)
gof2 <- sienaGOF(ansnull, IndegreeDistribution, varName ="friendship", join = FALSE)
p1 <- plot(gof1, period = 1)
p2 <- plot(gof2, period = 1)
gridExtra::grid.arrange(p1, p2)
# sum(gof1$`Period 1`$SimulatedTestStat >= gof1$`Period 1`$ObservedTestStat)/1000
# [1] 0.154
# > sum(gof2$`Period 1`$SimulatedTestStat >= gof2$`Period 1`$ObservedTestStat)/1000
# [1] 0.063

@@

<<adjmatviz, fig.align='center', fig.cap="A visualization of the adjacency matrices of the three waves of network observations in the ``Teenage Friends and Lifestyle Study'' data. The subset we will be using is outlined in red.", fig.width=8, results='hide',fig.show='asis', fig.width=8, fig.height=3>>=
source("code/00e_small_friends.R")
view_rs2$wave <- factor(view_rs2$wave)
levels(view_rs2$wave) <- c("Wave 1", "Wave 2", "Wave 3")
ggplot(data= view_rs2, aes(x = x, y=y)) + 
  geom_tile(aes(fill = as.factor(value))) + 
  scale_fill_manual("i likes j", labels=c("no", "yes"), 
                    values = c('white', 'black')) +
  geom_rect(data= NULL, inherit.aes = FALSE, color = 'red',
            aes(xmin = 19.5, xmax = 35.5, ymin = 19.5, ymax = 35.5, fill =NA)) + 
  facet_wrap(~wave) + theme_bw() +
  labs(x = "i", y = "j") + 
  ThemeNoNet + 
  theme(aspect.ratio=1, axis.text = element_blank(), axis.ticks = element_blank()) 
@

>>>>

<<sienagof, fig.cap="Goodness of fit measures for two network statisticscomputed on the first simulated wave of a SAOM: indegree and outdegree cumulative distributions. On the x-axis is the degree value, and on the y-axis is the number of times that degree value occurs in the network. \\st{The p-value shown on the x-axis is the proportion of observations simulated from the model that have observed statistic values as large or larger than the values observed in the data.}", cache = TRUE, message = FALSE, warning = FALSE, fig.height=5>>=
load("data/ansnullpaper.rda")
library(lattice)
gof1 <- sienaGOF(ansnull, OutdegreeDistribution, varName ="friendship", join = FALSE)
gof2 <- sienaGOF(ansnull, IndegreeDistribution, varName ="friendship", join = FALSE)
p1 <- plot(gof1, period = 1)
p2 <- plot(gof2, period = 1)
gridExtra::grid.arrange(p1, p2)
# sum(gof1$`Period 1`$SimulatedTestStat >= gof1$`Period 1`$ObservedTestStat)/1000
# [1] 0.154
# > sum(gof2$`Period 1`$SimulatedTestStat >= gof2$`Period 1`$ObservedTestStat)/1000
# [1] 0.063

@@

<<adjmatviz, fig.align='center', fig.cap="A visualization of the adjacency matrices of the three waves of network observations in the ``Teenage Friends and Lifestyle Study'' data. The subset we will be using is outlined in red.", fig.width=8, results='hide',fig.show='asis', fig.width=8, fig.height=3>>=
source("code/00e_small_friends.R")
view_rs2$wave <- factor(view_rs2$wave)
levels(view_rs2$wave) <- c("Wave 1", "Wave 2", "Wave 3")
ggplot(data= view_rs2, aes(x = y, y=-x)) + 
  geom_tile(aes(fill = as.factor(value))) + 
  scale_fill_manual("i likes j", labels=c("no", "yes"), 
                    values = c('white', 'black')) +
  geom_rect(data= NULL, inherit.aes = FALSE, color = 'red',
            aes(xmin = 19.5, xmax = 35.5, ymax = -19.5, ymin = -35.5, fill =NA)) + 
  facet_wrap(~wave) + theme_bw() +
  labs(x = "j", y = "i") + 
  ThemeNoNet + 
  theme(aspect.ratio=1, axis.text = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank()) 
@
